\documentclass[11pt,draft,letterpaper,compsoc]{IEEEtran}
\usepackage{enumerate}
\usepackage{color}
\usepackage[dvipdf,dvips]{graphicx}
\usepackage{epstopdf}
\usepackage{subfigure}
\usepackage[cmex10]{amsmath}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{url}

\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
\title{BU ECE Dept. MSc Proposal\\ CloudWatch: An Open Cloud Monitoring Environment}

\author{Qingqing~Li (U20626734) \\ (Advisor(s): Prof.~Orran~Krieger, Dr. Ata Turk)\\ [8mm]Student Signature:\\ [8mm] Advisor Signature: \\ [8mm]}

\IEEEcompsoctitleabstractindextext{%
\begin{abstract}

Cloud computing has many intrinsic advantages as well as some challenges, such as performance unpredictability. Public cloud, which is usually owned by a single provider, is rather opaque to users. It does not provide information at hardware level to users, which restricts users' decision making when experimenting in clouds. This kind of data can only be obtained through monitoring the cloud and carefully retaining the data. We will use Massachusetts Open Cloud (MOC) as our cloud environment. MOC is the first cloud that aims at letting many vendors participate in a cloud, in which monitoring can be more meaningful, for the reason that users will have more choices, such as brands, in MOC environment. We propose that exposing some extent of data to users can help them to make wise choices. This project will be separated to two parts. The first part, Data Collection and Retention, will be a platform building phase that collects and stores raw data generated from MOC. It will be a two-month work with another master student in his project--'Open Cloud for Cloud Research'. The second part, Data Visualization, will be the completion of the platform by filtering and exposing the data collected in a readable and meaningful way. We will provide users with an API for efficient queries of the data. A visualization that shows the MOC's physical information and also a specific mapping between physical resources and virtual resources for each user.

\end{abstract}

\begin{IEEEkeywords}
    Monitoring, Cloud, MOC, Visualization.
\end{IEEEkeywords}}

% make the title area
\maketitle

\IEEEdisplaynotcompsoctitleabstractindextext

\IEEEpeerreviewmaketitle

\input{Sections/Section1-ProblemStatement.tex}
\input{Sections/Section2-PriorWork.tex}
\input{Sections/Section3-ProposedApproach.tex}
\input{Sections/Section4-Plan.tex}

\bibliographystyle{ieeetr}
\bibliography{main}

\end{document}