\documentclass[11pt,draft,letterpaper,compsoc]{IEEEtran}
\usepackage{enumerate}
\usepackage{color}
\usepackage[dvipdf,dvips]{graphicx}
\usepackage{epstopdf}
\usepackage{subfigure}
\usepackage[cmex10]{amsmath}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{url}

\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
\title{BU ECE Dept. MSc Proposal\\ Open Cloud for Cloud Research}

\author{Hua~Li (U-1460-8155) \\ (Advisor(s): Prof.~Orran~Krieger, Dr. Ata Turk)}

\IEEEcompsoctitleabstractindextext{%
\begin{abstract}

With the rapid growth and wide adoption of cloud computing, the complexity of cloud infrastructures is increasing with a lot of challenges, on which the research community and industry are investing large mount of resources. One challenge is provision and continutiy of application performance, which is critical to both cloud privider and cloud usesr, because that means reliable service, cost efficiency. For application performance optimization, there have been numerous researches about prediction of performance, which helps administrators and users make decision of resources sheduling, planning and allocation. Most of these researches come up with prediction methods with high accuracy. However, they are ususally either cloud provider specific or application specific requiring huge extra works to apply them to actual sheduling or planning, moreover, and these studies ususally cost the researchers a lot repeative intensive works in collecting data from cloud for experiments. Instead of spending large amount resources and works in answering questions like: what the performance it will be if this kind of application is running on my VMs. Given that the cloud provider can answer these questions, it will bring great value and innovation to the cloud users and research community. For example, cloud provider can make suggestion to user on the configuration of the VMs that is most efficient for specific application to help usesrs make accurate placemnt descion to achieve high performance. However, this is still an illusion which needs the research community and industry work together to realize it. To achieve this, two of the challenges are (i) performance measurements of cloud infrastructures and (ii) categorization of different applications in cloud. For completion of this M.S. project, we will build a platform to collect and retain measurements data from cloud and develop a tool to categorize the applications running in a VM.

\end{abstract}

\begin{IEEEkeywords}
    Monitoring, Cloud, MOC, Categorization, Performance.
\end{IEEEkeywords}}

% make the title area
\maketitle

\IEEEdisplaynotcompsoctitleabstractindextext

\IEEEpeerreviewmaketitle

\input{Sections/Section1-ProblemStatement.tex}
\input{Sections/Section2-PriorWork.tex}
\input{Sections/Section3-ProposedApproach.tex}
\input{Sections/Section4-Plan.tex}

\bibliographystyle{ieeetr}
\bibliography{main}

\end{document}
