\section{Plan and Schedule}
\label{sec:Plan}

\begin{itemize}
\item{[Sep 2015 - Oct 2015]:} Data collection. 1) Evaluate various monitoring tools, and choose one or several tools that satisfy our project requirements including performance, scalability, elasticity. Collect physical system information of MOC using monitoring tools we chose. 2) Evaluate metering tools for OpenStack, such as Ceilometer and StackTach. Use the metering tool that better suits our needs and also produce less overhead, and collect per-tenant information for virtual resources usage. 
\item{[Oct 2015 - Nov 2015]:}Data retention. 1) We will evaluate several databases and choose databases that suits our needs. 2) We will also need to evaluate centralized or distributed database storage system for our environment and design data schema. 3) We will integrate the monitoring tools and our storage.
\item{[Nov 2015 - Dec 2015]:} Explore the metrics that users are interested in by doing researches. Store more data as we know more about users demands. Maintain the database so that we can do queries on larger set of data that is generated and collected from the cloud. 
\item{[Dec 2015 - Jan 2016]:} Design and write the API for users that they can use for more convenient queries. If we decide to use several databases, we will also write APIs that set up connections among different databases. 
\item{[Jan 2016 - Feb 2016]:} Continuing writing APIs for users.  
\item{[Feb 2016 - Mar 2016]:} Using the data we collect and stored in the database, we need to make a visualization tool that can visualize both physical system information and a mapping between physical resources and virtual resources for each user. During this month, the visualization of the whole cloud, how the physical devices are connected and what are conditions of physical machines will be provided.  
\item{[Mar 2016 - Apr 2016]:} Continuing in making the visualization tool. The visualization of mapping between physical resources and virtual resources will be provided to users during this phase.  
\item{[Apr 2016 - May 2016]:} Refine all parts of the project. Write the report.
\end{itemize}
